Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-17 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
修改拼写错误

Let $V=\{I_i\}_1^T$ denote the frames of a video sequence of length $T$.
$B^{gt}=\{b^{gt}_i\}_1^T$ is used to represent the target's ground-truth position in each frame.
The visual object tracking will predict the position $B^{pred}=\{b^{pred}_i\}_1^T$ of this target in the subsequent frames when given its initial state.
In SiamFC++ \cite{SiamFC++}, the tracker first transforms the reference frame $I_1$ and annotation $b_1^{gt}$ to get an template image $\textbf z$, and transforms the candidate frame $I_i$ to get the search image $\textbf x_i$ centered at the position obtained in the previous frame.
At each time-step, the template image $\textbf z$ and the search image $\textbf x_i$ are first passed individually through a shared backbone network, and the resulting features are processed by some non-shared layers and fused by depth-wise separable correlation. The fused features then act as input to a head network, which predicts a classification map $\textbf{C}$, a bounding box regression map $\textbf{R}$, and a quality assessment map $\textbf{Q}$. In short, $\textbf C$ encodes the probability of each spatial position to contain a the target, $\textbf R$ regresses the bounding box position of the target, and $\textbf Q$ predicts the target state estimation quality. The final bounding box is then generated according to $\textbf{C}$, $\textbf{R}$ and $\textbf{Q}$.

>>>>

Let $V=\{I_i\}_1^T$ denote the frames of a video sequence of length $T$.
$B^{gt}=\{b^{gt}_i\}_1^T$ is used to represent the target's ground-truth position in each frame.
The visual object tracking will predict the position $B^{pred}=\{b^{pred}_i\}_1^T$ of this target in the subsequent frames when given its initial state.
In SiamFC++ \cite{SiamFC++}, the tracker first transforms the reference frame $I_1$ and annotation $b_1^{gt}$ to get an template image $\textbf z$, and transforms the candidate frame $I_i$ to get the search image $\textbf x_i$ centered at the position obtained in the previous frame.
At each time-step, the template image $\textbf z$ and the search image $\textbf x_i$ are first passed individually through a shared backbone network, and the resulting features are processed by some non-shared layers and fused by depth-wise separable correlation. The fused features then act as input to a head network, which predicts a classification map $\textbf{C}$, a bounding box regression map $\textbf{R}$, and a quality assessment map $\textbf{Q}$. In short, $\textbf C$ encodes the probability of each spatial position to contain the target, $\textbf R$ regresses the bounding box position of the target, and $\textbf Q$ predicts the target state estimation quality. The final bounding box is then generated according to $\textbf{C}$, $\textbf{R}$ and $\textbf{Q}$.
